Supporting Information Appendix:\\ Black-swan events in animal populations

### 2017-03-22 text/supp.tex
Final minor tweaks to figures and supplement

The following pseudo R code illustrates the procedure to generate process
noise with effective $\nu$ values within a CV of 0.2 of the specified value
(the actual code is available at
\url{https://github.com/seananderson/heavy-tails}):

@@

\section{Code availability} Data and code to reproduce our analysis are
available at\\ \url{https://github.com/seananderson/heavy-tails}

>>>>

The following pseudo R code illustrates the procedure to generate process
noise with effective $\nu$ values within a CV of 0.2 of the specified value:

@@

\section{Code availability} Data and code to reproduce our analysis are
available at\\ \url{https://github.com/seananderson/heavy-tails}\\ and are archived at\\ \url{http://doi.org/10.5281/zenodo.321930}
